### 2016-05-31 w-wires/paper_gerasimovda.tex
Estimation for integral at y < Z, plots
More proofs!

\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcH}{\mathcal{H}}
\newcommand{\bbT}{\mathbb{T}}
\newcommand{\bbC}{\mathbb{C}}
\newcommand{\bbD}{\mathbb{D}}

@@

First, we will compute a lower bound $l(k)$ for $s(k)$, such that $0 \le l(k) \le s(k)$. Then, we replace $s(k)$ with its lower bound under the integral sign and will prove convergence of this integral to $0$. This reasoning is valid since for $s(k) \le 1$, $\ln l(k) \le \ln s(k)$.

\subsubsection{Computing $s(k)$}
First, notice that $s(k)$ is periodic w.r.t. real axis.
\todo{Plot of $\abs{\det S}$ ?}
% Since $\sin k$ and $\cos k$ are periodic w.r.t the real axis, with the period of $2 \pi$, 
\todo{is this step really necessary?}

@@

\begin{align*}
s_1(x + \iu y)
 &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}} && \text{(since $\cosh y \ge 1$)}\\
 &= \abs{\frac{\tanh y - V}{\tanh y + V}}
\end{align*}

Note that now $s_1(k)$ has zeroes along the line $\Im k = Z$, which means $\ln s_1(k)$ will have continuous number of singularities along this line. However, we'll show that the function is still integrable.

@@

Next, since $\tanh y \ge 0$ for $y \ge 0$ and is strictly increasing, we can get rid of the absolute value:

\todo{make the formula bigger}
\[
s_1(x + \iu y)
 = \begin{cases}
 \frac{V - \tanh y}{\tanh y + V}, & 0 \le y \le Z \\
 \frac{\tanh y - V}{\tanh y + V}, & y > Z 
 \end{cases}
\]

Now, the estimation splits in two cases:

\subsubsection*{Case 1: $0 \le y \le Z$}
We will estimate the function from below by a piecewise function containing of two pieces. We do that by noticing that the function is convex on $0 \le y \le Z$ and can be approximated from below with its first derivative at $0$ and at $Z$. 
\todo{this step is necessary because we have to $\ln f(z)$ is zero in vicinity of 0}

\[
f(y) = 
\begin{cases}
s_1'(0) y + 1   &, 0 \le y < Z_0  \\
s_1'(Z) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
=
\begin{cases}
\frac{-2}{V} y + 1   &, 0 \le y < Z_0  \\
\frac{1}{2 V}(V^2 - 1) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\]

Since denominator $\tanh y + V$ only increases as $0 \le y \le Z$, we can replace it with its maximum value $\tanh Z + V = 2 V$, thus getting estimate $s_2$:

\[
s_2(x + \iu y) = \frac{V - \tanh y}{2 V} = \frac{1}{2} - \frac{1}{2 V} \tanh y \le s_1(x + \iu y)
\]

Since $\tanh(y)$ is concave, $s_2$ is convex \todo{proof} on $0 \le y \le Z$, we can approximate it from below using its first derivative at $Z$:

\[
s_3(x + \iu y) = s_2'(Z)(y - Z) = \frac{{\left(W^{2} - 1\right)}^{2}}{4 \, {\left(W^{2} + 1\right)} W} (Z - y)
\]
% \[
% h'(Z) = \frac{{\left(W^{2} - 1\right)}^{2}}{4 \, {\left(W^{2} + 1\right)} W}
% \]
% h'(W=2) = 9/40; h'(W=3) = 8/15

Since $s_3$ is stricly decreasing, $s(0) = \frac{{\left(W^{2} - 1\right)}^{2}}{4 \, {\left(W^{2} + 1\right)} W} Z$ is strictly positive and $s(Z) = 0$, $s_3(k)$ is non-negative and $\ln s_3(k)$ is well defined on $0 \le y \le Z$.

\todo{We might need one more estimate to ensure $l(x + 0 \iu) = 1$}

@@

\begin{align*}
    & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C)^2} dy \\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + y^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\end{align*}

@@

\todo{first part}

@@

\begin{align*} 
    & \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\le & \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + Z)}} \frac{1}{\sqrt{(R + C - C)}} dy\\
=   & \frac{1}{\sqrt{R - C + Z}} \frac{R}{\sqrt{R}}  \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{1}{R^2 - C^2 + 2 C y} dy\\
\end{align*}

>>>>

\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcO}{\mathcal{O}}
\newcommand{\mcH}{\mathcal{H}}
\newcommand{\bbT}{\mathbb{T}}
\newcommand{\bbC}{\mathbb{C}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbD}{\mathbb{D}}

@@

If we use $s(k)$ directly, it is not possible to evaluate integral analytically. However, $s(k)$ has nice properly of being an absolute value of the determinant of $S$-matrix, which means $0 \le s(k) \le 1$. This means we are free to replace $s(k)$ with a lower bound $l(k)$ such that $0 \le l(k) \le s(k)$, and prove convergence of the resulting integral to $0$ instead. This reasoning is valid since for $s(k) \le 1$, $\ln l(k) \le \ln s(k) \le 0$. We are going to rely on this fact heavily and use simple functions (e.g. piecewise linear) or simple known bounds for logarith to estimate the original integral.

\subsubsection{Computing $l(k)$}
First, we will simplify $s(k)$ across all of the upper complex plane and make it independent of real part of the argument.

Notice that $s(k)$ is periodic w.r.t. real axis.
\todo{Plot of $\abs{\det S}$ ?}
% Since $\sin k$ and $\cos k$ are periodic w.r.t the real axis, with the period of $2 \pi$, 
\todo{is this step really necessary?}

@@

\begin{align*}
l_1(x + \iu y)
 &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}} && \text{(since $\cosh y \ge 1$)}\\
 &= \abs{\frac{\tanh y - V}{\tanh y + V}}
\end{align*}

Note that now $l_1(k)$ has zeroes along the line $\Im k = Z$, which means $\ln l_1(k)$ will have continuous number of singularities along this line. Intuitively, it shouldn't spoil anything, because the integration contour might have or have not crossed a singularity of $\ln s(k)$ anyway. And indeed, we'll show that the function is still integrable.

@@

Next, since $\tanh y$ is non-negative and strictly incresing for $y \ge 0$, we can get rid of the absolute value:

\todo{make the formula bigger}
\[
l_1(x + \iu y)
 = \begin{cases}
 \frac{V - \tanh y}{\tanh y + V}, & 0 \le y \le Z \\
 \frac{\tanh y - V}{\tanh y + V}, & y > Z 
 \end{cases}
\]

Next, we split the estimation in two separate cases (below/above the singularity):

\subsubsection*{Case 1: $0 \le y \le Z$}
Crucial property of $s(k)$ as $\Im k$ gets close to $0$ is that it gets close to $1$. This is very important, since it implies that $\ln s(k)$ goes to $0$, which is essential part of convergence of the integral. Intuitively, the contour gets closer and closer to the real axis, so if $\ln s(k)$ did not nullify on $\bbR$, we wouldn't have convergence to zero. So, a sensible lower bound of $s(k)$ should respect that property as well and converge to $1$ as $\Im k \to 0$.

Since the function is convex on $0 \le y \le Z$, it can be approximated from below with its first derivative at $0$. However, just this will violate the \todo{positiveness??} property, so we have to approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:

\begin{align*}
f(y)
& = 
\begin{cases}
s_1'(0) y + 1   &, 0 \le y < Z_0  \\
s_1'(Z) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\\
& =
\begin{cases}
\frac{-2}{V} y + 1   &, 0 \le y < Z_0  \\
\frac{1}{2 V}(V^2 - 1) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\end{align*}

Notice that the estimate does not necessarily has to be continuous, so any $Z_0$ works as long as the estimate is positive definite. However for computational convenience $Z_0 = \frac{V}{4}$ suits our needs best \todo{prove?}.

\subsection*{$0 \le y < \frac{V}{4}$}

We compute the upper bound for the integrand \todo{$\int\limits_{y = C - R }^{V/4}$ }.

\[
\ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R - C + y}} \frac{1}{\sqrt{R + C - y}}
\]

We use the inequality $\frac{x}{1 + x} \le \ln (1 + x)$ for $x > -1$, where $x = -\frac{2}{V} y$. In this case, since the argument of the logarithm is less than $1$, $(1 + x)^2 \le \frac{x^2}{(1 + x)^2}$.

\[
\le \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2} \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R - C + y}} \frac{1}{\sqrt{R + C - y}}
\]

Replace $1 - \frac{2}{V}y$ with its minimum value $0.5$ and $R + C - y$ with its minimum value $R + C - \frac{V}{4}$.

\todo{dammit, finish this}

\subsection*{$\frac{V}{4} \le y < Z$}

\[
\ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R - C + y}} \frac{1}{\sqrt{R + C - y}}
\]

Replace:
\begin{itemize}
\item $R^2 - C^2 + 2 (C + 1) y + 1$ with its minimum value $R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1$
\item $R - C + y$ with its minimum value $R - C + \frac{V}{4}$
\item $R + C - y$ with its minimum value $R + C - Z$
\end{itemize}

Function $\ln^2(x)$ is integrable in the neighbourhood of $0$ and it is well known \todo{reference?} that

\[
\int\limits_{x=x_0}^b \ln^2(a (x - b)) dx = (b - x_0) (\ln^2(a (x_0 - b)) - 2 \ln(a (x_0 - b)) + 2)
\]

In our case, $x_0 = \frac{V}{4}$, $b = Z$, therefore the integral is bounded by constant independent of $R$ and $C$. Therefore, the behaviour of the function is defined by the behaviour of its multiplier before the integral:

\[
\frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R - C + \frac{V}{4}}} \frac{1}{\sqrt{R + C - Z}}
\]

As $r \to \infty$, clearly $R \to \infty$, $C \to \infty$, $R - C \to 0$ and one can easily see that the expression above is $\mcO(\frac{1}{\sqrt{R + C}})$, therefore, zero in the limit.

@@

\begin{align*}
    & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y + 1} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\end{align*}

@@

First part:
\begin{align*} 
    & \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\le & \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + Z)}} \frac{1}{\sqrt{(R + C - C)}} dy\\
=   & \frac{1}{\sqrt{R - C + Z}} \frac{R}{\sqrt{R}}  \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{1}{R^2 - C^2 + 2 C y} dy\\
\end{align*}

@@
